### 2012-12-04 inst/examples/policycosts/quick_examples.Rmd
caching for quick_examples, run on one
code for variance and autocorrelation, as per Fig 4

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor=element_line(colour="transparent"))
theme_set(theme_notebook)
```

@@

```{r apples}
apples <- c(L2=1.034, L1=1.724, free_decrease=1.724, fixed=8.276, free_increase=1.724)
xtable(apples)
````

@@

Solve the policy cost for the specified penalty function

@@

``` {r simulate_policy, dependson=c("L1", "L2", "free_increase", "free_decrease", "fixed", "quad_costs")}
sims <- list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy$D, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none, seed=seed)
)
````

@@

``` {r p0, dependson="tidy"}
p0 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1) +
  geom_line(aes(time, harvest, col=penalty_fn, lty=penalty_fn))+ 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p0
```

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

```{r p2, dependson="tidy", fig.width=12}
p2 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_wrap(~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
````

>>>>

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="quick_examples/")
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

Actually, we'll want to draw these from the table in figure4 data at different levels.  
Ideally we can draw the policy out rather than running that again.

```{r apples}
apples <- c(L2=1.034, L1=1.724, free_decrease=1.724, fixed=8.276, free_increase=1.724)
````

@@

Solve the policy cost for the specified penalty function.

@@

``` {r simulate_policy, dependson=c("L1", "L2", "free_increase", "free_decrease", "fixed", "quad_costs")}
seed
sims <- list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy$D, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none, seed=seed)
)
````

@@

``` {r p0, dependson="tidy"}
p0 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1) +
  geom_line(aes(time, harvest, col=penalty_fn, lty=penalty_fn))+ 
  labs(x="time", y="stock size", title = "Stock Dynamics")

p0
```

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")

p1
```

```{r p2, dependson="tidy", fig.width=12}
p2 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_wrap(~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")

p2
````

Calculate statistics of the kind used in figure 4.

```{r}
dt[,var(harvest), by=penalty_fn]
dt[,acf(harvest, lag.max=1, plot=F)$acf[2], by=penalty_fn]
```
